NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-28 paper/application.tex
update relate works

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the 
To illustrate how the proposed perturbation-driven exploration tool help the domain experts interpret the neural network model,
summarized  and interpret the attention mechanism.
These scenarios are summarized by the domain experts who integrating the proposed tool into their model analysis workflow.

\subsection{Scenario 1: Interpreting Decision Making Process}
Understanding the decision making process, i.e., why the model make a prediction, is most crucial aspect in model analysis.
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the 
To better illustrate how the proposed perturbation-driven exploration tool helps the domain experts interpret the neural network model, we present five application scenarios, which summarized by the domain experts who integrated the proposed tool into their model analysis workflow.

\subsection{Scenario 1: Interpreting Decision Making Process}
Understanding why the model make a given prediction is of great interests to the domain expert, 
since interpreting decision making processing is not only essential for evaluating the model performance but also necessary for hypothesizing improvement strategies.
%
The three stages (encoder, attention, classifier) of the model work in synergy to produce the correct prediction.
%
%One of the essential task for can be made in either of these stages.
% \shusen{difference in sensitivity among entail natural and contradict relationships}
% the generate the correct prediction for the wrong reason

### 2018-03-28 paper/relatedWorks.tex
update relate works

\textbf{Model Interpretability.}
Before one can solve the model interpretability challenge, it worth to define what constitutes an explanation or interpretation of a machine learning model.
As discussed in ~\cite{Lipton2016, Doshi-Velez2017}, despite the concept of interpretable is inherently subjective, it is still necessary to refine the concept and devise guidelines for approaching model interpretability problems.
%And as suggested in~\cite{Doshi-Velez2017}
In machine learning community, one of the most studied areas in model interpretability is the interpretation of convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
%
These methods either identify the pattern that maximally activate a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures), or reveal what areas in the input contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
%
Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which make them applicable to different applications. In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understanding snapshot of the classifier near a specific input.
%
Despite being invaluable for generating a human understandable explanation, however, the lack of the ability to access and explore the internal states of the system limits their application. 
%which is vitally important for making sense of the inner works of a model, 
To avoid similar limitation, the proposed system enabled direct access and manipulation of the internal of the model.

>>>>

\textbf{Model Interpretability.}
Before one can solve the model interpretability challenge, it worth to understand what constitutes an explanation for a machine learning model.
As discussion in~\cite{Lipton2016, Doshi-Velez2017}, there is little consensus on what interpretability is in the context of machine learning. A taxonomy is suggested~\cite{Doshi-Velez2017} to promote a more rigorous study on such a subject. In the work by Lipton~\cite{Lipton2016}, many philosophical questions related to model interpretability are examined and the study also challenged the commonly held belief that linear models are more interpretable than deep neural networks.
%
In machine learning community, one of the most studied areas in model interpretability is the interpretation of convolution neural network (CNN) ~\cite{SimonyanVedaldiZisserman2013, ZeilerFergus2014, YosinskiCluneNguyen2015, OlahMordvintsevSchubert2017, OlahSatyanarayanJohnson2018}.
%
These methods either identify the pattern that maximally activate a part of the network (referred to as \emph{feature visualization}, i.e., what feature does the given neuron, channel, or layer captures), or reveal what areas in the input that contribute most to the predicted label (often referred to as \emph{attribution}, i.e., attribute the prediction label in the input domain).
%
Besides the techniques designed for specific types of models, a few works~\cite{RibeiroSinghGuestrin2016, LundbergLee2017} approach the interpretability challenge from a model agnostic perspective, which make them applicable to different applications. In the LIME~\cite{RibeiroSinghGuestrin2016} work, a simpler linear model is fitted near the prediction of interests to provide a simpler but easier to understanding snapshot of the classifier near a specific input.
%
Despite being invaluable for generating a human understandable explanation, however, the lack of the ability to access and explore the internal states of the system limits their application. 
%which is vitally important for making sense of the inner works of a model, 
To avoid similar limitation, the proposed system enabled direct access and manipulation of the internal of the model.
